Trends of SDR in Thessaloniki

### 2023-05-25 Article_B138.Rmd
Commit 2023-05-25 18:17

author:
  - name:        Natsis Athanasios
    email:       natsisphysicist@gmail.com
    affiliation: Laboratory of Atmospheric Physics, AUTH
    correspondingauthor: true
    footnote: 1
  - name:        Alkiviadis Bais
    email:       bob@example.com
    affiliation: Another University
address:
  - code: Some Institute of Technology
    organization: Big Wig University
    addressline: 1 main street
    city: Gotham
    state: State
    postcode: 123456
    country: United States
  - code: Another University
    organization: Department
    addressline: A street 29
    postcode: 2054 NX
    city: Manchester,
    country: The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

>>>>

author:
  - name:        Natsis Athanasios
    email:       natsisphysicist@gmail.com
    affiliation: Laboratory of Atmospheric Physics, AUTH
    correspondingauthor: true
    footnote:    1
  - name:        Alkiviadis Bais
    email:       bob@example.com
    affiliation: Another University
address:
  - code:         Aristotle University of Thessaloniki
    organization: Big Wig University
    addressline:  1 main street
    city:         Thessaloniki
    state: State
    postcode: 123456
    country:      Greece
  - code:         Another University
    organization: Department
    addressline: A street 29
    postcode:    2054 NX
    city:        Manchester,
    country:     The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
